Numerical Stability of Detonations in White Dwarf Simulations

### 2019-02-23 papers/ignition/paper.tex
Add some discussion of whether previous papers were converged

Early studies on WD collisions \citep{rosswog:2009,raskin:2010,loren-aguilar:2010,
hawley:2012,garcia-senz:2013} typically had effective spatial resolutions in the
range 100--500 km for the grid codes, and 10--100 km for the SPH codes, and observed
detonations that convert a large amount of carbon/oxygen material into iron-group elements.
These studies varied in methodology (Lagrangian versus Eulerian evolution, nuclear network
used) and did not closely agree on the final result of the event (see Table 4 of
\cite{garcia-senz:2013} for a summary). \cite{kushnir:2013} argued that many of these
simulations featured numerically unstable evolution, ultimately caused by the zone size
being significantly larger than the length scale over which detonations form. The detonation
length scale can vary widely based on physical conditions \citep{seitenzahl:2009,garg:2017}
but is generally not larger than 10 km.

>>>>

Early studies on WD collisions \citep{rosswog:2009,raskin:2010,loren-aguilar:2010,
hawley:2012,garcia-senz:2013} typically had effective spatial resolutions in the
range 100--500 km for the grid codes, and 10--100 km for the SPH codes, and observed
detonations that convert a large amount of carbon/oxygen material into iron-group elements.
These studies varied in methodology (Lagrangian versus Eulerian evolution, nuclear network
used) and did not closely agree on the final result of the event (see Table 4 of
\cite{garcia-senz:2013} for a summary).

\added{There is mixed evidence for simulation convergence presented in these studies.
\cite{raskin:2010} claim that their simulations are converged in nickel yield up to 2 million
(constant mass) particles (Figure 11 in that paper), but the nickel yield still appears to be
trending slightly upward with particle count. The simulations from \cite{raskin:2009} are not
converged up to 800,000 particles (Figure 4 in that paper), where the smoothing length was kept
constant instead of the particle mass. \cite{hawley:2012} do not achieve convergence over a
factor of 2 in spatial resolution (Figure 8 in that paper). \cite{garcia-senz:2013} claim at
least qualitative (though not strict absolute) convergence in Section 3.2 of their paper, but
their convergence test is only over a factor of 2 in particle count, which is a factor of 1.26
in spatial resolution for constant mass particles. \cite{kushnir:2013} test convergence over an
order of magnitude in spatial resolution, and find results that appear to be reasonably well
converged for one of the two codes used (VULCAN2D), and results that are not converged for the
other code (FLASH). \cite{papish:2015} claim convergence in nuclear burning up to 10\% at a
resolution of 5--10 km, but do not present specific data demonstrating this claim.
\cite{loren-aguilar:2010} and \cite{rosswog:2009} do not present convergence studies for
their work.}

\cite{kushnir:2013} argued that many of these simulations featured numerically unstable evolution,
ultimately caused by the zone size being significantly larger than the length scale over which
detonations form. The detonation length scale can vary widely based on physical conditions
\citep{seitenzahl:2009,garg:2017} but is generally not larger than 10 km. \added{\citeauthor{kushnir:2013}
argue that this numerically unstable evolution is the primary cause of convergence difficulties.
They further argue that it is possible to apply a burning limiter to achieve converged results,
which was used in both their work and the simulations of \cite{papish:2015}. We will investigate
this hypothesis in \autoref{sec:unstable_burning}.}
